---
title: "Storage K -1"

output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: false
    toc_depth: 2
    # number_sections: true
    #theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#library(icon)
library(kableExtra)
```

```{r include=FALSE}

# loading the main table from csv
lista_consumabili <- read.csv2("consumabili_270521.csv", header = TRUE)

colnames(lista_consumabili) <- c("", "Volume", "Bags / Box", "n° per bag / box", "Total", "filter_name")

# subsetting the main table
plastic_tubes <- subset(lista_consumabili, filter_name == "plastic_tubes")

plastic_tips <- subset(lista_consumabili, filter_name == "plastic_tips")

syringes <- subset(lista_consumabili, filter_name == "syringes")

glass_tubes <- subset(lista_consumabili, filter_name == "glass_tubes")

petri <- subset(lista_consumabili, filter_name == "petri")

colnames(petri) <- c("", "Diameter", "Bags / Box", "n° per bag / box", "Total", "filter_name")

falcon <- subset(lista_consumabili, filter_name == "falcon")

paper_filters <- subset(lista_consumabili, filter_name == "paper_filters")

pasteur <- subset(lista_consumabili, filter_name == "pasteur")

cuvettes <- subset(lista_consumabili, filter_name == "cuvettes")

plastic_pots <- subset(lista_consumabili, filter_name == "plastic_pots")

tecan <- subset(lista_consumabili, filter_name == "tecan")
```

### Last update: 15 / 06 / 2022
#### for any update (deposit or withdrawal), please email me! --> [Mauro](mailto:mauro.maver@unibz.it?subject=[Update]%20Storage%20K-1%20and%20Lab%201.20)

---

### Last changes:
- 15/06/2022 - List updated - **Mauro**
- 05/04/2022 - 100x Epp. 5mL, 60x Falcon 15mL, 350x Falcon 50mL removed - **Fabio** 
- 27/01/2022 - List updated - **Mauro**
- 13/01/2022 - List updated - **Mauro**
- 05/01/2022 - List updated - **Mauro**
- 25/11/2021 - 900x Falcon 50mL, 60x Falcon 15mL, 60x Epp. 5mL, 300x Epp. 2mL, 180x Glass tubes, 340x Cuvettes removed - **Oussama**
- 24/11/2021 - 520x Falcon 50mL, 600x  Falcon 15mL removed - **Marco**
- 23/11/2021 - 100x Falcon 15mL, 200x Epp. 5 mL removed - **Fabio**
- 28/10/2021 - 80 Tecan plates added - **Mauro**
- 27/09/2021 - Syringes and filters added - **Mauro**
- 07/09/2021 - List updated - **Mauro**
- 14/05/2021 - List updated - **Mauro**
- 28/05/2021 - List created - **Mauro**

---

### To buy:
- falcon 15 mL
- falcon 50 mL
- paper filters

---

## Plastic tubes

```{r echo=FALSE}
plastic_tubes[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Plastic tips

```{r echo=FALSE}
plastic_tips[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Falcon tubes

```{r echo=FALSE}
falcon[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Syringes

```{r echo=FALSE}
syringes[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Glass tubes (mineralization)

```{r echo=FALSE}
glass_tubes[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Petri dishes

```{r echo=FALSE}
petri[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Paper filters

```{r echo=FALSE}
paper_filters[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Cuvettes

```{r echo=FALSE}
cuvettes[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Pasteur

```{r echo=FALSE}
pasteur[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Plastic pots

```{r echo=FALSE}
plastic_pots[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

## Tecan plates

```{r echo=FALSE}
tecan[,1:5] %>%
  kable(row.names = FALSE, align = "l") %>%
  kable_styling(bootstrap_options = c("striped", "hover","responsive", "condensed"),font_size = 16)
```

